True versus apparent shapes of astrophysical bow shocks

### 2017-03-30 papers/Paper1/sec-quadrics-observations.tex
Start to discuss correlations of size with other parameters

@@

@@

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.8\textwidth]{figs/mipsgal-pairplot}
  \caption[]{Matrix of pair plots that illustrate distributions of and
    correlations between the non-shape parameters of all MIPSGAL bow
    shock sources from \citet{Kobulnicky:2016a}.  Plots on the leading
    diagonal show histograms of the following parameters: bow shock
    angular size, \(\log_{10} R_0\); Galactic latitude,
    \(\log_{10}|b|\); Galactic longitude, \(\cos \ell\);
    extinction-corrected \(H\)-band magnitud of the stellar source,
    \(H_0\); \(K\)-band extinction, \(A_K\).  Scatter plots in the
    upper triangle show the joint distribution of each pair of
    parameters.  These are repeated in the lower triangle but showing
    the KDEs of the joint distributions, which are annotated with the
    Pearson linear correlation coefficient, \(r\), for each pair. The
    straight lines shown superimposed on the plots of stellar magnitud
    versus bowshock size correspond to model results for the same star
    at a sequence of distances (dashed lines) and a sequence of
    stellar luminosities at a fixed distance (dotted lines).  See text
    for details. }
  \label{fig:mipsgal-pairplot}
\end{figure*}

@@

The catalog gives the \(K\)-band extinction, \(A_K\), derived using
the method of \citet{Majewski:2011a}, but that assumes an intrinsic
color of \((H - [\SI{4.5}{\um}])_0 = +0.08\) magnitudes, which is too
red if the sources are assumed to be OB stars.  We therefore re-derive
\(A_K\) from the catalog magnitudes combined with the
\citet{Indebetouw:2005a} reddening law, but assuming
\((H - [\SI{4.5}{\um}])_0 = -0.1\) magnitudes, which is more typical
of early type stars.  This does not make very much difference (compare
the top-right plot of our Fig.~\ref{fig:mipsgal-pairplot} with
\citeauthor{Kobulnicky:2016a}'s Fig.~9), but it does eliminate some of
the apparent negative extinctions that are found in the catalog.

@@

>>>>

\subsubsection{Automatic tracing and fitting of bow shocks}
\label{sec:autom-trac-fitt}

@@

\subsubsection{Subjective evaluation of the fit quality}
\label{sec:subj-eval-fit}

@@

\subsubsection{OB bow shock shapes on the diagnostic plane}
\label{sec:ob-shapes}

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.8\textwidth]{figs/mipsgal-pairplot}
  \caption[]{Matrix of pair plots that illustrate distributions of and
    correlations between the non-shape parameters of all MIPSGAL bow
    shock sources from \citet{Kobulnicky:2016a}.  Plots on the leading
    diagonal show histograms of the following parameters: bow shock
    angular size, \(\log_{10} R_0\); Galactic latitude,
    \(\log_{10}|b|\); Galactic longitude, \(\cos \ell\);
    extinction-corrected \(H\)-band magnitude of the stellar source,
    \(H_0\); \(K\)-band extinction, \(A_K\).  Scatter plots in the
    upper triangle show the joint distribution of each pair of
    parameters.  These are repeated in the lower triangle but showing
    the KDEs of the joint distributions, which are annotated with the
    Pearson linear correlation coefficient, \(r\), for each pair. The
    straight lines shown superimposed on the plots of stellar magnitud
    versus bowshock size correspond to model results for the same star
    at a sequence of distances (dashed lines) and a sequence of
    stellar luminosities at a fixed distance (dotted lines).  See text
    for details. }
  \label{fig:mipsgal-pairplot}
\end{figure*}

\subsubsection{Correlation between bow shock size and other parameters}
\label{sec:corr-size}

@@

The catalog gives the \(K\)-band extinction, \(A_K\), derived using
the method of \citet{Majewski:2011a}, but that assumes an intrinsic
color of \((H - [\SI{4.5}{\um}])_0 = +0.08\) magnitudes, which is too
red if the sources are assumed to be OB stars.  We therefore re-derive
\(A_K\) from the catalog magnitudes combined with the
\citet{Indebetouw:2005a} reddening law, but assuming
\((H - [\SI{4.5}{\um}])_0 = -0.1\) magnitudes, which is more typical
of early type stars.  This does not make very much difference (compare
the top-right plot of our Fig.~\ref{fig:mipsgal-pairplot} with
\citeauthor{Kobulnicky:2016a}'s Fig.~9), but it does eliminate some of
the apparent negative extinctions that are found in the catalog.  The
same reddening law gives \(A_H = 1.55 A_K\), and this is used to
derive extinction-corrected \(H\)-band apparent magnitudes, \(H_0\).

The most significant linear correlation between any pair of parameters
in Figure~\ref{fig:mipsgal-pairplot} is that between bow shock size
and stellar source brightness: \(H_0\) versus \(\log_{10} R_0\), with
correlation coefficient \(r = -0.43\).  The distribution of \(H_0\)
depends on the absolute magnitude, \(M_H\), and the distance, \(d\),
to the source.  It is likely that variation in \(d\) is the more
important of the two because \(M_H\) changes relatively little for
main-sequence OB stars, ranging from \(M_H \approx -4\) (early-O) to
\(M_H \approx -1.5\) (mid-B).  This is because part of the increase in
bolometric luminosity, \(L\), is offset by an increase in the
effective temperature, \(T_{\text{eff}}\), which shifts the peak of
the stellar spectrum farther away from the \(H\)~band, resulting in
\(L_H \propto L / T_{\text{eff}}^3 \sim L^{0.53}\), where the last step uses
the upper main-sequence mass--luminosity and mass--radius scalings from
\citet{Eker:2015a}. It is true that evolved OB supergiants can be much
brighter, reaching \(M_H \approx -7\), but such stars are expected to be
rare.  Assuming a B2V star (\(M_H = -2\)), then the observed range
\(H_0 = 5\)--\(12\) corresponds to distances
\(d = 100\)--\SI{6300}{pc}, and the histogram peak at
\(H_0 \approx 9.5\) corresponds to \(d \approx \SI{2000}{pc}\), which is all
perfectly reasonable.

Turning now to the distribution of bow shock angular size, \(R_0\),
this may be affected by various factors:
\begin{enumerate}[1.]
\item Distance, \(d\), since for a constant physical size the angular
  size will vary as \(R_0 \propto d\).
\item Momentum-loss ratio, \(\beta\), between the two flows that form the
  bow shock.  All other things being equal, we have
  \(R_0 \propto \beta^{1/2}\).  If the environment flow is constant and the OB
  star wind has mass-loss rate \(\dot{M}\) and terminal velocity
  \(V_\infty\), then \(\beta \propto \dot{M}{V_\infty}\).  Empirical and theoretical
  studies of hot star winds (e.g., \citealp{Puls:1996a}) imply
  \(\dot{M}{V_\infty} \sim L^{1.88} R^{-1/2} \sim L^{1.80}\), where the final
  step applies only to main-sequence stars and again uses the
  relations of \citet{Eker:2015a}.  
\end{enumerate}

\subsubsection{Correlation between bow shock shape and other parameters}
\label{sec:corr-shape}

@@

Mention future JWST observations with \(0.85\arcsec\) resolution at \SI{22}{\um}.
